---
title: "Using data visualization to find patterns in multidimensional data"
author: "Amelia McNamara @AmeliaMN"
date: "June 27, 2015"
output: ioslides_presentation
---

## About me
I'm an academic, so the techniques I am going to talk about come from academia. 

Here's an extra-credit question (tweet at me!): who is the research in common with all three methods I'm talking about today?

## Big data versus multidimensional data

I don't believe in big data, but I do believe in multidimensional data. 

## Generalized pairs plot

Do you know the scatterplot matrix or pairs plot? Generally, it looks like this:

```{r}
plot(mtcars)
```

## 

That's a lot to look at, so lets take a subset:
```{r, warning=FALSE, message=FALSE}
library(dplyr)
select(mtcars, mpg, cyl, disp) %>% plot()
```

## Generalized pairs plot (citation)

The pairs plot is useful on its own, but the generalized pairs plot is even better.

Emerson, J. W., Green, W. A., Schloerke, B., Crowley, J., Cook, D., Hofmann, H., and Wickham, H. (2013). The generalized pairs plot. Journal of Computational and Graphical Statistics, 22(1):79–91. 

[http://bit.ly/gpairs](http://bit.ly/gpairs)

## 

```{r}
library(gpairs)
gpairs(mtcars)
```

## Grand Tour

The Grand Tour lets you explore multidimensional data more genericly. 
```{r, echo=FALSE}
library(knitr)
opts_knit$set(animation.fun = hook_scianimator)
knit_hooks$set(custom_plot = hook_plot_custom)
```

```{r, custom_plot = TRUE, fig.ext='png', echo=FALSE}
library(tourr)
tourr::render(flea[, 1:6], grand_tour(d = 2), display = display_xy(), frames=30, dev="png", fig_path(".png"))
Sys.sleep(1)
```

## Graphical inference



